raptr: Representative and Adequate Prioritization Toolkit in R

### 2016-11-26 code/rmarkdown/figures.Rmd
+ update checkpoint date to use raptr 0.0.3

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-11-01', R.version='3.3.1', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))

>>>>

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-11-26', R.version='3.3.1', scanForPackages=FALSE)
try(session::restore.session('data/final/results.rda'))

### 2016-11-26 code/rmarkdown/text.Rmd
+ update checkpoint date to use raptr 0.0.3

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-11-01', R.version='3.3.1', scanForPackages=FALSE)
session::restore.session('data/final/results.rda')

>>>>

```{r, include=FALSE}
## initialization
# load .rda file
checkpoint::checkpoint('2016-11-26', R.version='3.3.1', scanForPackages=FALSE)
session::restore.session('data/final/results.rda')
